---
title: "Basline models for Dynamic Hedge"
author: "Xin Jing"
date: "2017年6月8日"
output: html_document
---

# remember to import library("rugarch") before running the program

# CCC Dynamic Hedge(Training set)
```{r,eval=TRUE, echo=FALSE}
library("readxl")

testing_size = 80
data = read_excel("/Users/xinjing/Desktop/dynamic hedge/CAD.xlsx")
basis = data$log_spot - data$log_futures
basis = basis[1:(length(basis)- testing_size - 1)]
basis_matrix =  matrix(basis,nrow = length(basis),ncol = 1,byrow = TRUE)

s = data$diff_spot[2:length(data$diff_spot)]
s = s[1:(length(s)-testing_size)]
s_matrix = matrix(s,nrow = length(s),ncol = 1,byrow = TRUE)
f = data$diff_futures[2:length(data$diff_futures)]
f = f[1:(length(f)-testing_size)]
f_matrix = matrix(f,nrow = length(s),ncol = 1,byrow = TRUE)
spec1= ugarchspec(variance.model=list(model="sGARCH"), mean.model=list(armaOrder=c(0,0), include.mean = TRUE, external.regressors = basis_matrix))
fit1=ugarchfit(data=s_matrix,spec=spec1,solver = "nloptr")
# Convergence of fit1
convergence(fit1)
fit2=ugarchfit(data=f_matrix,spec=spec1,solver = "nloptr")
# Convergence of fit2
convergence(fit2)
res1 = residuals(fit1)
res2 = residuals(fit2)
corr = cor(res1,res2)[1]
sigma1 = sigma(fit1)
sigma2 = sigma(fit2)
cov = sigma1 * sigma2 * corr
best = cov / (sigma2**2)
b = cov(s,f) / var(f)
# Without Hedging:
var(s)
# Naive Hedge:
var(s - f)
# Conventional Hedge:
var(s - b*f)
# Dynamic Hedge:
var(s - best*f)
```

# EUR:
# Without Hedging: 3.483064e-05
# Naive Hedge: 6.443201e-06
# Conventional Hedge: 6.027845e-06
# Dynamic Hedge:  6.202285e-06
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 10, within 5 epochs, average results after three trials: 6.22746105869044e-06


# ASD:
# Without Hedging: 4.933627e-05
# Naive Hedge:1.011334e-05
# Conventional Hedge: 9.495456e-06
# Dynamic Hedge: 1.006463e-05
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 10, within 3 epochs, average results after three trials: 9.782057585304154e-06


# BP:
# Without Hedging: 3.383008e-05
# Naive Hedge:3.943364e-06
# Conventional Hedge: 3.876226e-06
# Dynamic Hedge: 3.684688e-06
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 15, within 3 epochs, average results after three trials: 3.886130780029696e-06


# SP500:
# Without Hedging:6.82476e-05
# Naive Hedge: 6.332187e-06
# Conventional Hedge:  5.170403e-06
# Dynamic Hedge:  5.624029e-06
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 10, within 3 epochs, average results after three trials: 5.2223841114187975e-06(very stable)


# CAD:
# Without Hedging:2.551384e-05
# Naive Hedge: 4.062306e-06
# Conventional Hedge: 3.896271e-06
# Dynamic Hedge:  4.080657e-06
# Using LSTM, RNN1(only past prices changes), batch = 1, time step = 4,hidden units = 10, within 3 epochs, average results after three trials: 3.964477105875235e-06(very stable)


# CCC Dynamic Hedge(Testing set)
```{r,eval=TRUE, echo=FALSE}
library("readxl")
data = read_excel("/Users/xinjing/Desktop/dynamic hedge/BP.xlsx")
basis = data$log_spot - data$log_futures
basis = basis[1:(length(basis) - 1)]
# now length(basis) = length(s) - 1

s = data$diff_spot
s = s[2:length(s)]
f = data$diff_futures
f = f[2:length(f)]
# now length(basis) = length(s) = length(f)

static_ratios = c()
dynamic_ratios = c()

testing_size = 80
for (i in 0: (testing_size-1)) 
{# now getting the training set for each loop
 print(paste0("Current iteration:", i))
 basis1 = basis[1:(length(basis) - testing_size + i)]
 basis_matrix =  matrix(basis1,nrow = length(basis1),ncol = 1,byrow = TRUE)
 spec1= ugarchspec(variance.model=list(model="sGARCH",garchOrder = c(4, 4)),   mean.model=list(armaOrder=c(0,0), include.mean = TRUE, external.regressors = basis_matrix))
 s1 = s[1:(length(s) - testing_size + i)]
 s_matrix = matrix(s1,nrow = length(s1),ncol = 1,byrow = TRUE)
 f1 = f[1:(length(f) - testing_size + i)]
 f_matrix = matrix(f1,nrow = length(s1),ncol = 1,byrow = TRUE)
 fit1=ugarchfit(data=s_matrix,spec=spec1,solver = "nloptr")
 # Convergence of fit1
 convergence(fit1)
 fit2=ugarchfit(data=f_matrix,spec=spec1,solver = "nloptr")
 # Convergence of fit2
 convergence(fit2)
 sigma1 = sigma(fit1) # sigma of spot
 sigma2 = sigma(fit2) # sigma of futures
 coef1 = coef(fit1)
 coef2 = coef(fit2)
 resid1 = residuals(fit1)
 resid2 = residuals(fit2)
 corr = cor(resid1,resid2)[1]
 last_resid1 = resid1[length(resid1)]
 last_resid2 = resid2[length(resid2)]
 last_sigma1 = sigma1[length(sigma1)]
 last_sigma2 = sigma1[length(sigma2)]
 next_variance1 = coef1[3] + coef1[4]*(last_resid1**2) + coef1[5]*(last_sigma1**2)
 next_variance2 = coef2[3] + coef2[4]*(last_resid2**2) + coef2[5]*(last_sigma2**2)
 next_sigma1 = sqrt(next_variance1)
 next_sigma2 = sqrt(next_variance2)
 next_cov = next_sigma1 * next_sigma2 * corr
 # Conventional Hedge Ratio
 static_ratio = cov(s1,f1) / var(f1)
 # Dynamic Hedge Ratio
 dynamic_ratio = next_cov / (next_variance2) 
 
 static_ratios[i+1] <- static_ratio
 dynamic_ratios[i+1] <- dynamic_ratio
 }
testing_s = s[(length(s) - testing_size + 1) : length(s)]
testing_f = f[(length(f) - testing_size + 1) : length(f)]
# Without Hedging:
var(testing_s)
# Naive Hedge:
var(testing_s - testing_f)
# Conventional Hedge:
var(testing_s - static_ratios*testing_f)
# Dynamic Hedge:
var(testing_s - dynamic_ratios*testing_f)

```

# EUR:
# Without Hedging: 2.199741e-05
# Naive Hedge:2.708794e-07
# Conventional Hedge: 4.356389e-07
# Dynamic Hedge: 3.061782e-07
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 10, within 5 epochs, average results after three trials: 2.6410875148991017e-07


# ASD:
# Without Hedging: 2.633987e-05
# Naive Hedge: 7.066315e-07
# Conventional Hedge: 9.332773e-07
# Dynamic Hedge: 8.032848e-07
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 10, within 3 epochs, average results after three trials:7.029923778014998e-07


# BP:
# Without Hedging: 2.849907e-05
# Naive Hedge: 2.466863e-07
# Conventional Hedge: 2.719982e-07
# Dynamic Hedge: 2.770509e-07(garchOrder = c(1, 1)), 2.224645e-06(garchOrder = c(4, 4))
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 15, within 3 epochs, average results after three trials: 2.416891757521187e-07(very stable)


# SP500:
# Without Hedging: 6.538379e-05
# Naive Hedge: 6.636125e-06
# Conventional Hedge:  4.931073e-06
# Dynamic Hedge:  5.648445e-06
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 10, within 3 epochs, average results after three trials: 4.878123369557861e-06(very stable)


# CAD:
# Without Hedging: 1.630007e-05
# Naive Hedge:2.624907e-07
# Conventional Hedge: 2.411519e-07
# Dynamic Hedge: 2.392148e-07
# Using LSTM, RNN1(only past prices chages), batch = 1, time step = 4,hidden units = 5, within 3 epochs, average results after three trials: 2.2948679125396727e-07(very stable)


# remember to import library("rmgarch") before running the program
# DCC Dynamic Hedge(Testing set)
```{r,eval=TRUE, echo=FALSE}
library("readxl")
data = read_excel("/Users/xinjing/Desktop/dynamic hedge/SP500_for_dynamic_hedge_2.xlsx")
basis = data$log_spot - data$log_futures
basis = basis[1:(length(basis) - 1)]
# now length(basis) = length(s) - 1

s = data$diff_spot
s = s[2:length(s)]
f = data$diff_futures
f = f[2:length(f)]

# now length(basis) = length(s) = length(f)

#test of dynamic correlation: DCCtest by Engle And Sheppard
mat = data.frame(s,f)
DCCtest(mat, garchOrder = c(1,1), n.lags = 1, solver = "solnp", solver.control = list(), cluster = NULL, Z = NULL)

static_ratios = c()
dynamic_ratios = c()

testing_size = 80
for (i in 0: (testing_size-1)) 
{# now getting the training set for each loop
 print(paste0("Current iteration:", i))
 basis1 = basis[1:(length(basis) - testing_size + i)]
 basis_matrix =  matrix(basis1,nrow = length(basis1),ncol = 1,byrow = TRUE)
 spec1= ugarchspec(variance.model=list(model="sGARCH",garchOrder = c(1, 1)),   mean.model=list(armaOrder=c(0,0), include.mean = TRUE, external.regressors = basis_matrix))
 uspec = multispec(replicate(2, spec1))
 dcc.garch11.spec = dccspec(uspec,dccOrder = c(1,1),distribution = "mvnorm")
 s1 = s[1:(length(s) - testing_size + i)]
 s_matrix = matrix(s1,nrow = length(s1),ncol = 1,byrow = TRUE)
 f1 = f[1:(length(f) - testing_size + i)]
 f_matrix = matrix(f1,nrow = length(s1),ncol = 1,byrow = TRUE)
 # s_f_matrix = cbind(s_matrix,f_matrix)
 # s_f_matrix = data.frame(s_matrix,f_matrix)
 s_f_matrix = data.frame(s1,f1)
 dcc.fit = dccfit(dcc.garch11.spec, data = s_f_matrix,solver = c("nloptr","solnp"))
 
 dcc.fcst = dccforecast(dcc.fit, n.ahead=1) # it is checked that this is equivalent to 
                                            # the next period stats calculated by hand.
 cov_matrix = rcov(dcc.fcst)
 
 next_variance_s = cov_matrix[[1]][1]
 next_variance_f = cov_matrix[[1]][4]
 next_cov = cov_matrix[[1]][2]
 

 # Conventional Hedge Ratio
 static_ratio = cov(s1,f1) / var(f1)
 # DCC Dynamic Hedge Ratio
 dcc_dynamic_ratio = next_cov / (next_variance_f) 
 
 static_ratios[i+1] <- static_ratio
 dynamic_ratios[i+1] <- dcc_dynamic_ratio
 }
testing_s = s[(length(s) - testing_size + 1) : length(s)]
testing_f = f[(length(f) - testing_size + 1) : length(f)]
# Without Hedging:
var(testing_s)
# Naive Hedge:
var(testing_s - testing_f)
# Conventional Hedge:
var(testing_s - static_ratios*testing_f)
# DCC Dynamic Hedge:
var(testing_s - dynamic_ratios*testing_f)
```


# DCC Dynamic Hedge: results on the testing set

# EUR: 
# Without Hedging: 2.199741e-05
# Naive Hedge:2.708794e-07
# Conventional Hedge: 4.356389e-07
# Dynamic Hedge: 3.061782e-07
# DCC Dynamic Hedge: 3.146707e-07
# RNN: 2.6410875148991017e-07


# ASD: 
# Without Hedging: 2.633987e-05
# Naive Hedge: 7.066315e-07
# Conventional Hedge: 9.332773e-07
# Dynamic Hedge: 8.032848e-07
# DCC Dynamic Hedge:8.81595e-07
# RNN: 7.029923778014998e-07

# BP: 
# Without Hedging: 2.849907e-05
# Naive Hedge: 2.466863e-07
# Conventional Hedge: 2.719982e-07
# Dynamic Hedge: 2.770509e-07(garchOrder = c(1, 1)), 2.224645e-06(garchOrder = c(4, 4))
# DCC Dynamic Hedge:3.173687e-07
# RNN: 2.416891757521187e-07

# SP500: 
# Without Hedging: 6.538379e-05
# Naive Hedge: 6.636125e-06
# Conventional Hedge:  4.931073e-06
# Dynamic Hedge:  5.648445e-06
# DCC Dynamic Hedge:5.100829e-06
# RNN: 4.878123369557861e-06

# CAD: 
# Without Hedging: 1.630007e-05
# Naive Hedge:2.624907e-07
# Conventional Hedge: 2.411519e-07
# Dynamic Hedge: 2.392148e-07
# DCC Dynamic Hedge:2.835467e-07
# RNN: 2.2948679125396727e-07
